\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2014-11-26 proposal/mswp-proposal.tex
add text for google glass in chapter 5.

\chapter{3. Google Glass hack allows brainwave control}

>>>>

\chapter{3. Google Glass hack allows brainwave control}
After Google has released his Google Glass, a company called This Place, has developed a app to control the glass over brain waves. But the app alone is not enough to control the glass with the power of your mind. Normally the Goggle Glass is controlled over voice commands or over a touchpad built into the side of the device. To control the device with brain waves This Place combine the Google Glass with the Neurosky MindWave headset. The Neurosky MindWave is an EEG-headset to detect brain waves. This is one of the first devices for consumers. Normally this headset will be used to train your brain and it will be delivered with a hand full games. After combining the two devices, the company begins to testing what kind of brain waves they could detect. For this reason they create a simple app which implements a counter starting at 0. When the user concentrated, the app begin counting upwards towards 50. When the user starts to relaxe, the counter began returning to 0. After this successfully test, they want to develop an app to show a real-world use. So they developed MindRDR. It allows a user to take a photo and share it over Twitter only to use his mind. Very important to know is that the brain waves only activate the camera app at Google Glass and take a photo. The settings for Twitter were set before. They released their software for free, in hope that other developers can adapt it for other uses.
